\documentclass[letterpaper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}



%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Miles Benton}}\\
	milesbenton@gmail.com $\cdot$ (408) 300-2968 $\cdot$ https://github.com/kil0meters $\cdot$ https://linkedin.com/in/mebenton\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{California State University, Chico}\hfill Chico, CA\\
BS Computer Science \textit{GPA: 3.7} \hfill Aug 2021 - (May 2024)\\
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Association for Computing Machinery, Chico Chapter} \hfill Chico, CA\\
\textit{Vice President} \hfill Apr 2022 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Grew club from 4 active members to over 30.
	\item Created custom tooling to host programming competitions and weekly meetings.
  \item Helped organize school-wide programming competition.
\end{itemize}

\header{Projects}
{\textbf{chicoacm.org}} {\sl TypeScript, NextJS, Rust, WebAssembly, Docker, SQLite} \hfill https://github.com/kil0meters/acm\\
A competitive programming website with a focus on deterministic performance analysis.\\
    \begin{itemize}
      \item Safely executes arbitrary with minimal overhead by compiling code to \textbf{WebAssembly}.
      \item \textbf{Rust} backend split across multiple \textbf{Docker} containers hosted on \textbf{DigitalOcean}.
      \item Deterministic code timings allowing for competitive leaderboards.
    \end{itemize}

\vspace*{2mm}
{\textbf{SketchNexus}} {\sl TypeScript, SolidJS, WebSockets} \hfill https://sketchnexus.com\\
An online competitive drawing website featuring realtime communication via WebSockets.\\

    \begin{itemize}
      \item Elegant interface written in \textbf{TypeScript} that works on any screen size.
      \item Game viewer allowing users to analyze mistakes in their play.
      \item Noise-based position evaluation function to grade match outcomes.
    \end{itemize}

\vspace*{2mm}
{\textbf{Snail++}} {\sl Rust, WebAssembly, TypeScript} \hfill https://github.com/kil0meters/snailplusplus\\
An incremental game simulating the generation and solving of thousands of mazes in real time using highly optimized code.\\

    \begin{itemize}
      \item Combined \textbf{Rust/WebAssembly} and \textbf{TypeScript} architecture optimized for performance.
      \item Employed intensive \textbf{JavaScript} garbage collector optimizations to deliver consistent framerates even when simulating tens of thousands of mazes.
    \end{itemize}

\vspace*{2mm}

\header{Technical Skills}
\begin{tabular}{ l l }
	Programming Languages:    & Rust, C++, WebAssembly, TypeScript, SQL, Python \\
	Frameworks and Libraries: & React, NextJS, SolidJS, Actix                   \\
	Tools:                    & Git, Linux, Docker, SQLite, JWT, OAuth, CI/CD   \\
\end{tabular}
\vspace{2mm}

\header{Awards}
\textbf{Dean\textquotesingle{}s List} \hfill California State Univeristy, Chico\\
\hfill 2021/2022/2023\\
\vspace*{2mm}
\textbf{Chico Programming Competition} \hfill Association for Computing Machinery\\
Second Place \hfill Apr 2022\\
\textbf{Hackathon} \hfill Association for Computing Machinery- Women\\
https://github.com/kil0meters/ranker \hfill Apr 2023\\
\vspace*{2mm}

\
\end{document}
